Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-11 CAs_operads.tex
Corrections 3.3.2 et 4

    \caption{\footnotesize
    The sequences of the cardinalities, arity by arity, of the rewrite
    rules being completions of orientations of~$\CongrCAs{\gamma}$.}
    \label{tab:cardinalities_completion_CAs}
\end{table}
\Todo{S: erreur dans la table pour $\gamma = 1$ ? Il doit y avoir que
des $0$, j'ai corrigé. Vérifier.}
\Todo{S: il faut équilibrer la table. Toutes les suites doivent avoir
la même longueur. (ou alors, il est toléré d'avoir des suites plus
courtes à mesure que $\gamma$ augmente... mais non ici.)}
From these computer explorations, we conjecture that the algorithm we
use does not provide a finite convergent presentation of $\CAs{\gamma}$,
when $\gamma \geq 4$. We point out that for $\CAs{4}$ new rewrite
rules still appear in arity $42$. Moreover, the total number of rewrite
rules at this arity is~$3149$.
\medbreak

However, the completion algorithm we used depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$(\Tfr_1, \Tfr_2)$ which is not joinable, we recursively try to find a
completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ with one generator when
$\gamma \geq 4$. We discuss the cases with more than one generator in
the perspectives.
\medbreak

>>>>

    \caption{\footnotesize
    The sequences of the cardinalities, arity by arity, of the rewrite
    rules being completions of orientations of~$\CongrCAs{\gamma}$.}
    \label{tab:cardinalities_completion_CAs}
\end{table}
\Todo{S : il faut équilibrer la table. Toutes les suites doivent avoir
la même longueur. (ou alors, il est toléré d'avoir des suites plus
courtes à mesure que $\gamma$ augmente... mais non ici.)}
From these computer explorations, we conjecture that the algorithm we
use does not provide a finite convergent presentation of $\CAs{\gamma}$,
when $\gamma \geq 4$. We point out that for $\CAs{4}$ new rewrite
rules still appear in arity $42$. Moreover, the total number of rewrite
rules at this arity is~$3149$.
\medbreak

However, the completion algorithm we used depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$(\Tfr_1, \Tfr_2)$ which is not joinable, we recursively try to find a
completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ when $\gamma \geq 4$ and when
 the left and the right members of the rewriting rules are trees
 belonging to $\Mag$.
\medbreak
